%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data\&ML Engineer} % Job title
    {GetInData} % Organization
    {Poland, Remotely} % Location
    {08.2019 - \ldots} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Created and maintained ETL system based on AWS using Airflow, EMR, Spark and Glue.}
        \item {Implemeneted data anomalies detection module to alert about abnormal traffic.}
        \item {Designed and implemented systems for Machine Learning support (training, serving, scheduling) based on Kubeflow, Airflow, MLflow, Kedro and Seldon.}
        \item {Created and maintained MLOps system based on Google Cloud Vertex AI ecosystem.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Freelancer} % Job title
    {Self-employed} % Organization
    {Remotely} % Location
    {05.2018 - \ldots} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented Airflow-oriented data warehousing systems.}
        %\item {Deployed and maintained Hadoop on-premise Hadoop distirbutions.}
        \item {Implemented Kafka-based systems for streams ingestion, processing and visualisation using Kafka Streams, Connect, Druid and Superset.}
        \item {Optimized big data ETLs in PySpark and SparkR.}
        \item {Data science applications, including text mining.}
        %\item {Implemented Google Search Console data mining and ETLs to keep the insights up to date.}
        \item {Maintained EKS-based Datahub setup for metadata collection.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Data Engineer} % Job title
    {Fandom Inc.} % Organization
    {Poland, Remotely} % Location
    {08.2018 - 08.2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintained AWS-based data pipelines based on batch and streaming processes.}
        \item {Co-created Open Source projects related to data processing and querying.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Big Data Platform Expert} % Job title
    {DXC Technology} % Organization
    {Poland, Remotely} % Location
    {06.2017 - 07.2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Designed and created Big Data platforms system with Apache Kafka, Apache Hadoop and Apache Spark.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Data Engineer} % Job title
    {Allegro Group} % Organization
    {Toruń, Poland} % Location
    {04.2015 - 05.2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Co-created and maintained Big Data ecosystem based on Apache Hadoop and ETL between Apache Kafka and Hadoop.}
        \item {Conducted workshops on Apache Spark.}
        \item {Maintained recommendation and revelancy-targeting projects based on big data analysis.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior Java/PHP Developer} % Job title
    {Allegro Group} % Organization
    {Toruń, Poland} % Location
    {07.2010 - 03.2015} % Date(s)
    {
      %\begin{cvitems} % Description(s) of tasks/responsibilities
      %  \item {Implemented and maintained microservices for storing and serving files, operating on thumbnails and content validation.}
      %  \item {Co-created mobile sites.}
      %\end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
